### 2013-05-15 draft.tex
switched the order of the methods sections
added paragraph explaining cant do thin sections for all fossils

Most of the fossils were easily exposed by breaking the surrounding layers of poorly-lithified marl. For fossils in more strongly lithified beds, fossil material was accessed by cutting away the rock with a saw or microrotary drill. After fossils were separated from the rock, they were sonicated for two hours to remove residual sand, silt and mud from the surface of the fossils. Brachiopods, bryozoans, crinoids, gastropods and ostracods were sampled by flaking the surface of the skeleton or shell using a dental chisel. Every flake was visually inspected under a microscope at circa $25\times$ power. Flakes with visible pyrite grains or rough-textured recrystallized regions were rejected and not included in the material for analysis. For brachiopods, only the flakes preserving the characteristic fabric of the fibrous secondary layer were chosen for analysis (see Figure \ref{flakes}). Flakes were then sonicated briefly, rinsed, dried in a 50\degrees C oven, and powdered using a mortar and pestle. Only the apical ends of rugose corals were sampled, after removal of any micrite from the surface using an abrasive bit. The apical end was then cut off using a diamond microsaw, and powdered using a mortar and pestle. The apical ends of the corals were targeted because the coral septa are closely spaced together there, leaving less room for cement to precipitate between the septa. However, this sampling technique is still not as selective as the technique used for brachiopods, and may include more cement and sediment along with skeletal calcite. To assess diagenetic alteration, micrite and cement samples were drilled from cut surfaces and then powdered using a mortar and pestle.

@@

For electron backscatter diffraction (EBSD), 30 nm-thick uncovered, polished thin sections were obtained from cuts through the fossils. The thin sections were analyzed using the same SEM as above, under variable pressure vacuum, with an electron high tension of 20 kV. The stage was tilted 70$^{\circ}$. The AZtec program was used in $4\times4$ binning mode, with frame averaging over one frame. The step size was 2 $\mu$m for the rugose coral and 1.2 $\mu$m for the brachiopod. The electron beam interacts with the crystal and is diffracted in a characteristic pattern for calcite. The diffracted beam then interacts with the EBSD detector, depdending on the orientation of the calcite crystal. The data were analyzed using software from Oxford instruments.

@@

\bibliographystyle{garynat}
\bibliography{draft_05_08_13}

>>>>

Most of the fossils were easily exposed by breaking the surrounding layers of poorly-lithified marl. For fossils in more strongly lithified beds, fossil material was accessed by cutting away the rock with a saw or microrotary drill. After fossils were separated from the rock, they were sonicated for two hours to remove residual sand, silt and mud from the surface of the fossils. Brachiopods, bryozoans, crinoids, gastropods and ostracods were sampled by flaking the surface of the skeleton or shell using a dental chisel. Every flake was visually inspected under a microscope at circa $25\times$ power. Flakes with visible pyrite grains or rough-textured recrystallized regions were rejected and not included in the material for analysis. For brachiopods, only the flakes preserving the characteristic fabric of the fibrous secondary layer were chosen for analysis (see Figure \ref{flakes}). Flakes were then sonicated briefly, rinsed, dried in a 50\degrees C oven, and powdered using a mortar and pestle. Only the apical ends of rugose corals were sampled, after removal of any sediment from the surface using an abrasive bit. The apical end was then cut off using a diamond microsaw, and powdered using a mortar and pestle. The apical ends of the corals were targeted because the coral septa are closely spaced together there, leaving less room for cement to precipitate between the septa. However, this sampling technique is still not as selective as the technique used for brachiopods, and may include more cement and sediment along with skeletal calcite. Finally, to assess diagenetic alteration, micrite and cement samples were drilled from cut surfaces and then powdered using a mortar and pestle.

While all fossils were inspected under a microscope prior to sampling, we were not able to inspect all fossils in thin section, because carbonate clumped isotope measurements require large amounts of material, some of which is lost during preparation of thin sections. However, two representative brachiopods and rugose corals were examined in thin section. 30 $\mu$m-thick uncovered, polished thin sections were obtained from cuts through the fossils. These thin sections were examined first in transmitted and reflected light to characterize calcite textures, and were then characterized using several different spectroscopic techniques, described below.

For electron backscatter diffraction (EBSD),  The thin sections were analyzed using the same SEM as above, under variable pressure vacuum, with an electron high tension of 20 kV. The stage was tilted 70$^{\circ}$. The AZtec program was used in $4\times4$ binning mode, with frame averaging over one frame. The step size was 2 $\mu$m for the rugose coral and 1.2 $\mu$m for the brachiopod. The electron beam interacts with the crystal and is diffracted in a characteristic pattern for calcite. The diffracted beam then interacts with the EBSD detector, depdending on the orientation of the calcite crystal. The data were analyzed using software from Oxford instruments.

@@

@@

\bibliographystyle{garynat}
\bibliography{draft}
